\sysfull

### 2018-08-04 paper/asplos19/coalescing.tex
Energy guided

A very simple {\em energy-Oblivious} coalescing strategy treats all tasks as

@@

energy available to the device (i.e., variation in energy buffer size). 
Fig.~\ref{fig:energyBlind} shows how this strategy may experience a 
large number of repeated power failures without forward progress.
With the successful commit of each coalesced task sequence, the coalescing
target increases.  Eventually, the target may be too high and a coalesced task

@@

The strategy then slowly decreases the coalescing target, eventually reaching a

@@

in $f_\text{reboot}(B)$ and the increase in $f_\text{commit}(B)$.  If, after
some number $k$ successful commits the target must decrease back to its
original value before the $k$ commits, the algorithm must then decrease $B$ by
$k \times x$.  To accumulate this decrease, this strategy requires $k$ power
failures, after each of which the strategy decreases $B$ by $x$, eventually
decreasing by $k \times x$, but only after a long time. 

@@

\subsubsection{History-Guided Coalescing (HG)}

@@

The \emph{History-Guided} (HG) coalescing strategy adapts the coalescing target more
quickly, addressing a key limitation of the EO coalescing strategy.  
HG gives each task unity weight, as with EO.  
HG differs from EO in how it updates $B$ on commit, and after a power failure.
HG assumes that as the duration of execution since a power failure increases,
the amount of energy remaining decreases, and the risk of failing during a long
sequence of coalesced tasks increases.  
Consequently, HG decreases the coalescing target by half with each successful commit.
HG is {\em history-guided} because it initializes the coalescing target to be
equal to $H$, the total number of tasks executed between the most recent pair
of power failures.

@@

successfully commit $H$ tasks (i.e., to set $B = H$), HG conservatively sets $B$ equal to half
of $H$ moderating the risk of a very long coalesced task. 
The fraction of the history by which HG adjusts $B$ is arbitrary.
We experimented with a range of fraction values, settling on one half as the
default for HG, because one half had the highest performance.

The HG algorithm is characterized by the following functions: 
%
\begin{equation}
	\begin{split}
		 f_\text{reboot}(H) 			& = \lfloor(H / 2)\rfloor \\
		 f_\text{weight}(T_\text{i}) 	& =  1 \\
		 f_\text{commit}(B) 			& = \lfloor(B / 2)\rfloor
	\end{split}
\end{equation}
%
Fig.~\ref{fig:hg-coal} illustrates the operation of the history-guided
coalescing strategy.
The figure shows two power cycles following the $i$th, the latter having an
execution history $H^{(i)} = 4$.
Based on that, $B$ is initially set to two and then decreases to one. Once the
value of $B$ reaches one, HG is, in effect, expecting a power failure,
justifying the conservative approach. After the power failure, HG
uses the most recent history $H^{(i+1)} = 8$ to set $B = 4$
and continue execution.
%
\subsubsection{Weighted History-Guided Coalescing (WHG)}
\label{subsec:energyTaskAware}
%
The Weighted History-Guided (WHG) coalescing strategy accounts for the
different energy and time cost of a program's tasks when setting the coalescing
target.
%
Each different task in the program consumes a different amount of energy to
execute to completion.  
%
The EO and HG coalescing strategies assume each task has uniform energy cost:
for these strategies, $B$ simply corresponds to a target {\em count} of tasks
coalesced, regardless of the individual cost of each task.
%
However, if one task executes for ten seconds and another executes for one
second, counting tasks misjudges the amount of {\em work} in the coalesced
tasks.

>>>>

A very simple {\em energy-oblivious} coalescing strategy treats all tasks as

@@

energy available to the device. With the successful commit of each coalesced task sequence, the coalescing target increases.  Eventually, the target may be too high and a coalesced task

@@

The strategy then linearly decreases the coalescing target, eventually reaching a

@@

in $f_\text{reboot}$ and the increase in $f_\text{commit}$.  Let us assume $x=1$. If, after $k$ successful commits the target must decrease to its original value $B-k$ due to an energy drop, this strategy requires $k$ successive power failures.

@@

\subsubsection{Energy-Guided Coalescing (EG)}

@@

The \emph{Energy-Guided} (EG) coalescing strategy adapts its coalescing target more quickly, addressing a key limitation of the EO, to adhere to changes in energy conditions. It uses its recent execution history as 
mean to measure energy availability and alters its target accordingly.
By relying on the history of execution EG eliminates the problem of frequent power failures a single coalesced task. In fact EG can reduce its target to one from any coalesced target in at most two successive power failures. For instance, if the execution is interrupted after finishing a single task the history will be one ($H = 1$) and the target will be set to one also. 

@@

successfully commit $H$ tasks (i.e., to set $B = H$). EG conservatively sets $B$ equal to half of $H$ moderating the risk of a very long coalesced task. We experimented with a range of fraction values, settling on one half as the default for EG, because one half had the highest performance. The EG algorithm is characterized by the following functions: 
		 f_\text{reboot}(H) 			& = \lceil(H / 2)\rceil \\
		 f_\text{commit}(B) 			& = \lceil(B / 2)\rceil
Fig.~\ref{fig:hg-coal} illustrates the operation of the EG.
The figure shows two power cycles following the $i$th, the latter having an
execution history $H^{(i)} = 4$.
Based on that, $B$ is initially set to two and then decreases to one. Once the
value of $B$ reaches one, EG is, in effect, expecting a power failure,
justifying the conservative approach. After the power failure, EG
uses the most recent history $H^{(i+1)} = 8$ to set $B = 4$
and continue execution.
\subsubsection{Weighted History-Guided Coalescing (WHG)}
\label{subsec:energyTaskAware}
The Weighted History-Guided (WHG) coalescing strategy accounts for the
different energy and time cost of a program's tasks when setting the coalescing
target.
Each different task in the program consumes a different amount of energy to
execute to completion.  
The EO and HG coalescing strategies assume each task has uniform energy cost:
for these strategies, $B$ simply corresponds to a target {\em count} of tasks
coalesced, regardless of the individual cost of each task.
However, if one task executes for ten seconds and another executes for one
second, counting tasks misjudges the amount of {\em work} in the coalesced
tasks.
